Local simple connectedness of boundaries of hyperbolic groups

### 2020-03-10 paper.tex
Fixed some todos in section 2.3

\begin{lemma}\label{lem:boundedintersection}
  Let $C$ be a compact subset of $\boundary G - \set\xi$. Then the set of points 
  of intersection between $H$ and bi-infinite geodesics with one end point equal 
  to $\xi$ and the other in $C$ is bounded.
\end{lemma}

@@

The maps $q_i$ are described by the following lemma, which is immediate from
the definition of $p^\infty_i$.

@@

@@

\begin{proof}
  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so by
  Lemma~\ref{lem:describing_q_i} for each $i$ there is a geodesic ray
  $\alpha_i$ from $g_i$ to $\zeta_i$ that meets $N_{2\delta+1}^{g_i\cdot
  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$. After passing to a subsequence, the rays
  $\alpha_i$ converge uniformly on compact subsets to a bi-infinite geodesic
  from $\xi$ to some pint $\zeta \in C$ that does not meet $H$, contradicting
  Lemma~\ref{lem:geodesicsmeethorosphere}.
\end{proof}

@@

  \todo{Is the lemma strong enough?}
  In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
  $\delta$ of $x'$, for $i\geq i_0$. Furthermore, $\dist(g_i,x') = n_i$, so 
  $\dist(\eta_i(n_i), x')\leq 2\delta$. It follows from the description of
  $q_i$ in \cref{lem:describing_q_i} that $q_i(\zeta)$ is contained in a
  simplex with all vertices within a distance $4\delta+1$ of $x'$. The set of
  all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
  $q_{i_0}\restricted{C}$ are related by an affine homotopy for $i \geq i_0$. 
\end{proof}

@@

  Now, $\dist(x, H) \geq 9\delta+2$, so $\dist(z_j, H) \geq 5\delta+1$.
  Furthermore, $\gamma_j(n_i) \in H$. It follows that $\dist(\gamma_j(n_i), [z_1,
  z_2]) > \delta$ and so by considering a triangle with vertices $g_i$, $z_1$
  and $z_2$, $\dist(\gamma_1(n_i), \gamma_2(n_i)) \leq 2\delta$. The result
  follows by lemma~\ref{lem:describing_q_i}. 
  \todo{Is the lemma strong enough?}
\end{proof}

>>>>

\begin{lemma}\label{lem:bounded_intersection}
  Let $C$ be a compact subset of $\boundary G - \set\xi$. Then the set of points 
  of intersection between $H$ and bi-infinite geodesics with one end point equal 
  to $\xi$ and the other in $C$ is bounded.
\end{lemma}

@@

The maps $q_i$ are described by the following lemma.

@@

\begin{proof}
  This is immediate from the definition of the maps $p^\infty_{n_i}$. Note that
  the set has diameter at most $6\delta+1$, so does indeed span a simplex.
\end{proof}

@@

\begin{proof}
  \todo{Check the claim about neighbourhoods being equal.}
  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so by
  Lemma~\ref{lem:describing_q_i} for each $i$ there is a geodesic ray
  $\alpha_i$ from $g_i$ to $\zeta_i$ that meets $N_{2\delta+1}^{g_i\cdot
  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$, and so does not meet $H_i\intersection
  N_{i-4\delta-1}(v)$, which is equal to $H \intersection N_{i-4\delta-1}(v)$.
  After passing to a subsequence, the rays $\alpha_i$ converge uniformly on
  compact subsets to a bi-infinite geodesic from $\xi$ to some point $\zeta \in
  C$ that does not meet $H$, contradicting
  Lemma~\ref{lem:geodesicsmeethorosphere}.
\end{proof}

@@

  In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
  $\delta$ of $x'$, for $i\geq i_0$. Furthermore, $\dist(g_i,x') = n_i$, so 
  $\dist(\eta_i(n_i), x')\leq 2\delta$. It follows from the description of
  $q_i$ in \cref{lem:describing_q_i} that $q_i(\zeta)$ is contained in a
  simplex with all vertices within a distance $4\delta+1$ of $x'$. The set of
  all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
  $q_{i_0}\restricted{C}$ are related by an affine homotopy for $i \geq i_0$. 
\end{proof}

@@

  Now, $\dist(x, H) \geq 9\delta+2$, so $\dist(z_j, H) \geq 5\delta+1$.
  Furthermore, $\gamma_j(n_i) \in H$. It follows that $\dist(\gamma_j(n_i), [z_1,
  z_2]) > \delta$ and so by considering a triangle with vertices $g_i$, $z_1$
  and $z_2$, $\dist(\gamma_1(n_i), \gamma_2(n_i)) \leq 2\delta$. The result
  follows by lemma~\ref{lem:describing_q_i}. 
\end{proof}
